A Data-Driven Framework for Neural Field Modelling

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
commiting for merge

\subsection{State and Parameter Estimates} 
\label{sec:state_and_param_results}
To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 150 realisations of the data were generated. Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out. The initial state and parameters were unknown to the estimator. Ten iterations of the estimation algorithm were used to ensure the parameters  converged. Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure12.pdf}
\end{center}
\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}. Log of the RMSE of the kernel for different values of firing thereshold, $v_0$ and the slope of the sigmoid, $\varsigma$. Mean kernel estimates are obtained over 50 realisations in each case. red crosses indicate cases where the kernel can not be estimated due to numerical issues.}
\label{fig:Figure12}
\end{figure*}
\begin{figure*}[!ht]
\begin{center}

\includegraphics{./Graph/pdf/Figure13.pdf}
\end{center}
\caption{{\bf RMSE of the kernel estimates}. RMSE of the kernel for different values of sensor width, $\sigma^2_y$, distance between adjacent sensors is $\Delta_y=1.5$. Mean kernel estimates are obtained over 50 realisations in each case.}
\label{fig:Figure12}
\end{figure*}
\section*{Tables}

@@

\begin{table}[!ht]
\caption{
\bf{Parameters}}
\begin{tabular}{|c|l|c|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Delta$ & spatial discretisation step & 0.5 & mm \\
	$T_s$ & time step & $0.001$ & s\\
	$T$ & number of time steps used in estimation & 400 & n.a.\\
	\hline 
\multicolumn{4}{|c|}{\emph{Model}}\\
	\hline
	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
% 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
	$\varsigma$ & slope of sigmoidal activation function & 0.56 & mV$^{-1}$\\
	$v_0$ & firing threshold & 1.8 & mV \\
	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
	10 &-8 &0.5
	\end{array}
	\right]^{\top}$ & mV.spike$^{-1}$\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
	$N$ & number of sensors & 196 & n.a.\\ 
	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{N}$ & mm$^2$ \\
	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
	$\sigma_{d}$ & disturbance variance & 0.1 & mV \\
	\hline 
	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
	\hline
	$L$ & number of basis functions& 81 & n.a.\\
	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}}\\
	\hline
	$\rho_y$ & sensor over-sampling parameter & 1 & n.a.\\
	$\rho_\phi$ & field basis function over-sampling parameter & 1 & n.a.\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Estimation}}\\
	\hline
	$\alpha$& determines the spread of sigma points & 0.001 & n.a.\\
	$\beta$& prior knowledge of the sigma points distribution & 2 & n.a.\\
	$\kappa$& scaling parameter $(3-L)$& -78 & n.a.\\
	$\lambda$& scaling parameter & -80.99 & n.a.\\
	\hline
\end{tabular}
\begin{flushleft}Parameters for the neural field model, the model reduction, the frequency analysis and the estimation procedure.
\end{flushleft}
\label{tab:Parameters}
\end{table}

>>>>

\subsection{State and Parameter Estimates} 
\label{sec:state_and_param_results}
To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated. Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out. The initial state and parameters were unknown to the estimator. Eleven iterations of the estimation algorithm were used to ensure the parameters  converged. Figure~\ref{fig:Figure6} shows the rate of convergence, confirming the parameters converged, with the changes in the parameter errors falling to less than $10^{-4}$ after six iterations.

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure12.pdf}
\end{center}
\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}. Log of the RMSE of the kernel for different values of firing thereshold, $v_0$ and the slope of the sigmoid, $\varsigma$. Mean kernel estimates are obtained over 50 realisations in each case. red crosses indicate cases where the kernel can not be estimated due to numerical issues.}
\label{fig:Figure12}
\end{figure*}

% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{./Graph/pdf/Figure13.pdf}
% \end{center}
% \caption{{\bf RMSE of the kernel estimates}. RMSE of the kernel for different values of sensor width, $\sigma^2_y$, distance between adjacent sensors is $\Delta_y=1.5$. Mean kernel estimates are obtained over 50 realisations in each case.}
% \label{fig:Figure12}
% \end{figure*}

\section*{Tables}

@@

\begin{table}[!ht]
\caption{
\bf{Parameters}}
\begin{tabular}{|c|l|c|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Delta$ & spatial discretisation step & 0.5 & mm \\
	$T_s$ & time step & $0.001$ & s\\
	$T$ & number of time steps used in estimation & 400 & n.a.\\
	\hline 
\multicolumn{4}{|c|}{\emph{Model}}\\
	\hline
	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
% 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
	$\varsigma$ & slope of sigmoidal activation function & 0.8 & mV$^{-1}$\\
	$v_0$ & firing threshold & 2 & mV \\
	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
	10 &-8 &0.5
	\end{array}
	\right]^{\top}$ & mV.spike$^{-1}$\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
	$N$ & number of sensors & 196 & n.a.\\ 
	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{N}$ & mm$^2$ \\
	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
	$\sigma_{d}$ & disturbance variance & 0.1 & mV \\
	\hline 
	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
	\hline
	$L$ & number of basis functions& 81 & n.a.\\
	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}}\\
	\hline
	$\rho_y$ & sensor over-sampling parameter & 1 & n.a.\\
	$\rho_\phi$ & field basis function over-sampling parameter & 1 & n.a.\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Estimation}}\\
	\hline
	$\alpha$& determines the spread of sigma points & 0.001 & n.a.\\
	$\beta$& prior knowledge of the sigma points distribution & 2 & n.a.\\
	$\kappa$& scaling parameter $(3-L)$& -78 & n.a.\\
	$\lambda$& scaling parameter & -80.99 & n.a.\\
	\hline
\end{tabular}
\begin{flushleft}Parameters for the neural field model, the model reduction, the frequency analysis and the estimation procedure.
\end{flushleft}
\label{tab:Parameters}
\end{table}
